Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-21 paper_jasa.tex
experiment 3 choice reasons

>>>>

\begin{figure}[hbtp]
   \centering
       \scalebox{0.60}{\includegraphics{choice_reason.pdf}}
       \caption{Reasons for choosing the plot in a lineup for experiment 3. Reasons 1 = Most different plot,  2 = Visible trend,  3 = Clustering visible,  4= Other.  Reason 12 means both reasons 1 and 2 are chosen. Notice that 345 people choose only reason 3 out of whom 64\% got the actual plot (proportion correct = 0.64), which indicates there are number of people who choose the right plot for wrong reason (Type-III error). Those who chose reason 123 got the actual plot about 100\% times.}
       \label{fig:choice_reason}
\end{figure}
